### 2025-02-07 writing/manuscript.tex
update day 2

>>>>

\begin{table}[H]
  \caption{Summary Statistics by Treatment Status}
  \centering
  \begin{tabular}{lccc}
  \hline
  & Control & Treatment & $p$ \\
  \hline
  GPA (z-score) & 0.126 & 0.187 & 0.393 \\
  & (0.959) & (0.963) & \\
  [1ex]
  Reading Score (z-score) & 0.212 & 0.320 & 0.116 \\
  & (0.892) & (0.969) & \\
  [1ex]
  Math Score (z-score) & 0.285 & 0.307 & 0.753 \\
  & (0.900) & (0.978) & \\
  [1ex]
  Tie Strength & 3.982 & 3.923 & 0.892 \\
  & (6.041) & (5.613) & \\
  [1ex]
  Estrato & 1.670 & 1.693 & 0.623 \\
  & (0.633) & (0.633) & \\
  [1ex]
  Age & 20.576 & 20.733 & 0.380 \\
  & (2.410) & (2.423) & \\
  [1ex]
  Female & 0.529 & 0.531 & 0.947 \\
  & (0.500) & (0.500) & \\
  \hline
  Observations & 382 & 352 & \\
  \hline
  \end{tabular}
  \label{tab:treatment_stats}
  \end{table}

\begin{table}[H]
  \caption{Summary Statistics for Choice Set and Nominated Peers}
  \centering
  \begin{tabular}{lcccc}
  \hline
  & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
  \cline{2-5}
  & Choice Set & Nominated & Choice Set & Nominated \\
  \hline
  GPA (z-score) & -0.140 & 0.579 & -0.147 & 0.580 \\
  & (0.981) & (0.994) & (0.983) & (0.998) \\
  [1ex]
  Reading Score (z-score) & 0.167 & 0.547 & 0.166 & 0.501 \\
  & (0.902) & (0.883) & (0.903) & (0.910) \\
  [1ex]
  Math Score (z-score) & 0.202 & 0.513 & 0.206 & 0.624 \\
  & (0.883) & (0.918) & (0.885) & (0.941) \\
  [1ex]
  Tie Strength & 3.222 & 14.467 & 3.217 & 13.822 \\
  & (4.625) & (9.382) & (4.632) & (9.291) \\
  [1ex]
  Estrato & 1.817 & 1.738 & 1.811 & 1.725 \\
  & (0.672) & (0.648) & (0.672) & (0.647) \\
  [1ex]
  Age & 20.942 & 20.501 & 20.958 & 20.490 \\
  & (2.180) & (2.698) & (2.187) & (2.559) \\
  [1ex]
  Female & 0.524 & 0.562 & 0.520 & 0.428 \\
  & (0.499) & (0.497) & (0.500) & (0.495) \\
  \hline
  Observations & 128,847 & 673 & 128,150 & 669 \\
  \hline
  \end{tabular}
  \label{tab:stats_by_area}
  \end{table}
